---
title: "p8105_hw1_jl6325"
author: "Jianing Liu"
date: "2023-09-23"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Problem 1
```{r}

# This step is for install and load packages moderndive and tidyverse

library(moderndive)
library(tidyverse)
data("early_january_weather")
```


```{r}
weather <- early_january_weather
colnames(weather)
nrow(weather)
ncol(weather)
mean(weather$temp)
```
Description of this dataset:
From the output given above, we can see there are 15 variables listed from "colnames(weather)",
and there are 15 coloms and 358 rows of our dataset, and the mean temperature of this dataset
is 39.58212.

```{r}
ggplot(data = weather, 
       mapping = aes (x = time_hour, y = temp, color = humid)) + geom_point()
ggsave("temp_vs_hour_jl6325_ggplot.jpg")
```

As can be seen from the scatterplot generated above, the general trend in temperature has increased over time, and the higher the temperature the lower the humidity on the same day. Around January 14th , when temperatures rise significantly, humidity drops dramatically.

# Problem 2

```{r}
# Create all the variables
data_frame <- tibble(random_sample = rnorm(10),
                     logical_vector = random_sample > 0,
                     character_vector = c("C", "o", "l", "u", "m", "b", "i", "a", "No.", "One"),
                     factor_vector = c("A", "B", "C", "A", "B", "C", "A", "B", "C", "A"))
# Find the means
mean(pull(data_frame, random_sample))
mean(pull(data_frame, logical_vector))
mean(pull(data_frame, character_vector))
mean(pull(data_frame, factor_vector))

as.numeric(pull(data_frame, logical_vector))
as.numeric(pull(data_frame, character_vector))
as.numeric(pull(data_frame, factor_vector))
```

Based on the output from Problem 2, we can find the mean for random sample and logical vector,
but not for character vector and factor vector.
After we use as.numeric function, we can find that the logical vector shows 1 means greather
than 0 and 0 for samller than 0, but still not for character vector and factor vector since
they are not numeric values.